DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-01 ase2017/paper.tex
updated section

>>>>

For our experiments, we could observe that the \tool finds at least one controller sinthesized for our set of benchmarks in transfer-function and state-space representation.

We employed diverse set of real-world benchmarks. However, this set of benchmarks is limited within the scope of this paper, and the performance may not generalize to other bencharks. The media runtime for our benchmarks was 124s, and the average synthesis time amounts 35.5s for state-space benchamarks, while for transfer-function benchmark the average was 123.6s.

In particular, we can reproduce the stability property in the synthesized controller for a DC motor plant described in Eq.~\eqref{tf-synth-controller} simulating the step response in MATLAB. As can be seen, the Fig.~\ref{tf-step-response} shows that the controller synthesized using the \tool is stable, giving the reliability about the results of our tool.

\begin{equation}
\label{tf-synth-controller}
C(z)=\frac{-0.3466796875z+0.015625}{-0.5z^{2}+0.19921875z}.
\end{equation}

\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{tf-step-response.eps}
  \caption{Step response for the Eq.~\eqref{tf-synth-controller} describing a stable system for the DC motor plant.}
  \label{tf-step-response}
\end{figure}

Regarding the state-space representation, we can check in the plant expressed by Eq.~\eqref{ss-synth-controller} (that describes a system for pendulum) that the feedback matrix (represented by the Eq.~\eqref{ss-synth-feedback}) generated by \tool, when combined with the plant with the state equations described in Eq.~\eqref{ss-synth-controller} is also stable, as can been seen in Fig.~\ref{ss-step-response}.

\begin{equation}
\label{ss-synth-controller}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\
\end{equation}

Where,
%
$$A = \left[\begin{array}{cc}-1.999909737361046&-1.000000000000000\\1&0\end{array}\right],$$
$$B = \left [\begin{array}{c}4\\0\end{array}\right],$$
$$C = \left [\begin{array}{cc}-1.756887232846049&-1.7494556607764090\end{array}\right],$$
$$\quad D = \left [\begin{array}{c}9.8\end{array}\right].$$

\begin{equation}
\label{ss-synth-feedback}
\begin{split}
K &= \left [\begin{array}{cc}-0.5898&-0.1914\end{array}\right]
\end{split}\
\end{equation}

\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{ss-step-response.eps}
  \caption{Step response for the Eq.~\eqref{ss-synth-controller} describing a stable system for the pendulum plant.}
  \label{ss-step-response}
\end{figure}

The synthesized controllers are validated to be stable using the MATLAB approach, which means that our results are reliable for control engineers. A link to the full experimental environment, including the scripts to reproduce the results, all benchmarks and the tool, is provided in the footnoote on our website\footnote{\url{www.dsverifier.org}}.
